---
title: "Unttled"
output: html_document
date: "2025-01-27"
---

```{r Get Station Name}
# This is an example of creating a variable that can be used in-line to 
# populate our document. We did this cell together in class. Notice we are
# taking the first value of the 'name' column to find the name of the weather
# station.
weather <- read.csv("climate_2000.csv")
station_name <- weather$name[1]

```

In this document, we will analyze the weather data collected at the
`r station_name` weather station. We will use a series of questions to
perform a descriptive analysis on the dataset.

## Question 1 (2 points)

How many days of data were collected at the `r station_name` weather
station?

```{r number of days of data}
# Place your code here. I recommend that you use the unique() function to extract the 
# total number of dates in the data frame, and then use the length() function to 
# report the number of days. However, because this data is clean, you could just
# query the number of rows. Assign the result to the variable n_days.

# For example, I would do something like this:
# UNIQUE_DAYS <- unique(DATA_FRAME$DATE)
# N_DAYS <- length(UNIQUE_DAYS)

# Your code here ------------------------------------------------------
unique_days <- unique(weather$date)
n_days <- length(unique_days)
print(n_days)


# ---------------------------------------------------------------------
```

There were `r n_days` days of data collected at the `r station_name`
weather station.

## Question 2 (2 points)

What year was the data collected?

```{r year of data collection}
# Place your code here. Use the format() function to extract the year from the
# first date in the data frame. You will need to use the format string "%Y" as 
# the second argument. Assign the result to the variable data_year.

# For example, I would do something like this:
# FIRST_DATE <- DATA_FRAME$DATE[1]
# DATA_YEAR <- format(FIRST_DATE, "%Y")

# Your code here ------------------------------------------------------

first_date <- weather$date[1]
data_year <- format(first_date, "%Y")
print(data_year)



# ---------------------------------------------------------------------
```

The data was collected in `r data_year`.

## Question 3 (2 points)

How many days of rain and snow were there during the year `r data_year`?
Produce two values: one for rain, and one for snow.

```{r number of days of precipitation}
# In the data, notice that there are six columns that indicate whether or not
# there was precipitation on a given day: total_rain_mm, total_rain_flag, 
# total_snow_cm, total_snow_flag, total_precip_mm, and total_precip_flag. The 
# numeric columns contain a measurement of the amount of precipitation. The
# "flag" columns, on the other hand, are True if there is an amount of 
# precipitation that falls on that day, but is less than the minimum measurement.

# Leveraging what we know about logical values in R, this gives us an easy way 
# to compute the totals. We can make a logical statement that returns true if 
# the precipitation is greater than zero, or the total flag is true. 

# Use this method to get the total_days_of_snow, total_days_of_rain, and total_days_of_precipitation.


# For example, I would do something like this:
# TOTAL_DAYS_OF_SNOW <- sum(DATA_FRAME$NUMERIC_COLUMN > 0 | DATA_FRAME$BOOLEAN_COLUMN)
# And I would do the same for total days of rain.

# Your code here ------------------------------------------------------

total_days_of_snow <- sum(weather$total_snow_cm > 0 | weather$total_snow_flag)
print(total_days_of_snow)

total_days_of_rain <- sum(weather$total_rain_mm > 0 | weather$total_rain_flag)
print(total_days_of_rain)

total_days_of_percipitation <- sum(total_days_of_snow, total_days_of_rain)
print(total_days_of_percipitation)

# ---------------------------------------------------------------------
```

In `r data_year`, there were `r total_days_of_rain` days of rain, and
`r total_days_of_snow` days of snow.

## Question 4 (2 points)

What were the hottest and coldest temperatures, and when did they occur?

```{r hottest and coldest temperatures}
# Place your code here. Use the max() and min() functions to get the hottest
# and coldest temperatures, and assign them to the variables hottest_temp and
# coldest_temp. Then use the which() function to get the index of the hottest
# and coldest temperatures, and use that index to get the date of the hottest
# and coldest temperatures. Assign the dates to the variables hottest_temp_date
# and coldest_temp_date. 

# For example, I would do something like this:
# HOTTEST_TEMP <- max(DATA_FRAME$TEMPERATURE_COLUMN)
# HOTTEST_TEMP_DATE <- DATA_FRAME$DATE_COLUMN[which(DATA_FRAME$TEMPERATURE_COLUMN == HOTTEST_TEMP)]
# And I would do the same for the coldest temperature.

# Your code here ------------------------------------------------------
hottest_temp <- max(weather$max_temp_c)
print(hottest_temp)

coldest_temp <- min(weather$min_temp_c)
print(coldest_temp)

hottest_temp_date <- weather$date[which(weather$max_temp_c == hottest_temp)]
print(hottest_temp_date)

coldest_temp_date <- weather$date[which(weather$min_temp_c == coldest_temp)]
print(coldest_temp_date)


# ---------------------------------------------------------------------
```

The hottest temperature was `r hottest_temp` degrees, and it occurred on
`r hottest_temp_date`. The coldest temperature was `r coldest_temp`
degrees, and it occurred on `r coldest_temp_date`.

## Question 5 (2 points)

Plot the minimum and maximum temperatures for each day of the year
`r data_year`.

```{r min_max_temperature_graph, include=TRUE, echo=FALSE, fig.cap="Maximum and minimum temperatures."}
# Repeat the exercise we did in class. 

# Use the plot() function to create a line plot with the minimum and maximum 
#temperatures on the y-axis and the date on the x-axis. Maximum temperatures 
# should be red, minimums should be blue. Add a black line to indicate 0°C.

# For example, I would do something like this:
# plot(DATA_FRAME$X_COLUMN, DATA_FRAME$Y_COLUMN, type="l", col="red",
#      xlab = "date", ylab="temperature")ee

# lines(DATA_FRAME$X_COLUMN, DATA_FRAME$Y_COLUMN, type="l", col="blue")

# abline(h=VALUE, col="black")


# Your code here ------------------------------------------------------

plot(weather$date, weather$max_temp_c, type="l", col="red",
     xlab = "date", ylab="temperature")
lines(weather$date, weather$min_temp_c, type="l", col= "blue")

abline(h=0, col="black")


# ---------------------------------------------------------------------
```